\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-25 tex/ms.tex
still writing

As with the systematics model (\S\ref{sec:systematics}), the model
for the astrophysical signal is \emph{linear}: the total signal $\mathbf{a}$ 
is a linear operation on the vector of spherical harmonic coefficients 
that describes the body's surface:
%
\begin{align}
    \mathbf{a} = \mathbf{A} \mathbf{y}
\end{align}
%
where $\mathbf{A}$ is the design matrix \citep[equal to the quantity 
$\mathbf{s}^\top\mathcal{A}\mathbf{R}'\mathbf{R}$ in][]{Luger2019}
and $\mathbf{y}$ is the vector of spherical harmonic coefficients. As we will
see next, the linearity of the problem makes it easily invertible.

\subsection{Likelihood Function \& Inference}

Our full model for the flux in the $n^\mathrm{th}$ postage stamp is thus
%
\begin{align}
\mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
\end{align}
%
where $\circ$ denotes the element-wise product of two vectors.

@@

\todo{(present results with \& without time variability)}

@@

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_labels.pdf}
    \caption{\label{fig:map_labels}
             Labeled map of Sol d.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

No zonal cloud bands: prior.

>>>>

As with the systematics model (\S\ref{sec:systematics}), the model
for the astrophysical signal is \emph{linear}: the total signal $\mathbf{a}$ 
is a linear operation on the vector of spherical harmonic coefficients 
that describes the body's surface:
%
\begin{align}
    \mathbf{a} = \mathbf{A} \mathbf{y}
\end{align}
%
where $\mathbf{A}$ is the design matrix \citep[equal to the quantity 
$\mathbf{s}^\top\mathcal{A}\mathbf{R}'\mathbf{R}$ in][]{Luger2019}
and $\mathbf{y}$ is the vector of spherical harmonic coefficients. As we will
see below, the linearity of the problem makes it easily invertible.

Finally, for reference, in Figure~\ref{fig:starry_model} we plot the
\starry model for our maximum likelihood fit (\S\ref{sec:results}). The
sharp rise at the beginning of each orbit in Sector 1 is due to the changing
vantage point of \tess as Sol d transitions from a thin crescent to full phase.

\subsection{Full Model and Likelihood Function}

Our full model for the flux in the $n^\mathrm{th}$ postage stamp is
%
\begin{align}
\mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
\end{align}
%
where $\circ$ denotes the element-wise product of two vectors.

@@

@@

Figure~\ref{fig:model} shows the median model.  \todo{More on this here.}

The top panel of Figure~\ref{fig:map} shows the maximum likelihood map of Sol d.
\todo{More on this here.}

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_labels.pdf}
    \caption{\label{fig:map_labels}
             Map of Sol d with the major features indicated with suggested
             names.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

\todo{No zonal cloud bands: prior.}
